Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-07-10 main.tex
revise proof prop. closure and mv def. effectiveness

%The complexity of construction
\noindent
The construction time and size for $B_{A, T}$ are $O(\| T \|^3 . \| A \|^2)$,
where the sizes $\| T \|$ and $\| A \|$ are their number of states.
%of~$T$ is its number of states $|Q|$.
\florent{revise complexity with nb. of tr. and states}
%
The particular case of Proposition~\ref{prop:epsilon} for a singleton $A$,
\ie $A(s) = \one$ for a given $s$ and $A(s') = \zero$ for all $s' \neq s$,
corresponds to a construction of a \SWA for the partial application of a \SWT,
fixing the first argument $s$.
\begin{corollary} \label{cor:epsilon}
Given a \SWT $T$ over $\Sigma$, $\Delta$,
$\Semiring$ commutative, bounded and complete,
and $\bar\Phi$ effective,
and $s \in \Sigma^+$,
there exists an effectively constructible \SWA
$B_{s, T}$ over $\Delta$, $\Semiring$ and $\bar\Phi$,
such that for all $t \in \Delta^*$, $B_{s, T}(t) = T(s, t)$.
\end{corollary}

>>>>

%The complexity of construction
\noindent
The construction time and size for $B_{A, T}$ are $O(\| T \|^3 . \| A \|^2)$,
where the sizes $\| T \|$ and $\| A \|$ are their number of states.
%of~$T$ is its number of states $|Q|$.
\florent{revise complexity with nb. of tr. and states}
%
The particular case of Proposition~\ref{prop:epsilon} with a singleton $A$,
\ie such that $A(s) = \one$ for a given $s \in \Sigma^*$ 
and $A(s') = \zero$ for all $s' \neq s$,
corresponds to a construction of a \SWA for the partial application of the \SWT $T$,
fixing the first argument $s$.
\begin{corollary} \label{cor:epsilon}
Given a \SWT $T$ over $\Sigma$, $\Delta$,
$\Semiring$ commutative, bounded and complete,
and $\bar\Phi$ effective,
and $s \in \Sigma^+$,
there exists an effectively constructible \SWA
$B_{s, T}$ over $\Delta$, $\Semiring$ and $\bar\Phi$,
such that for all $t \in \Delta^*$, $B_{s, T}(t) = T(s, t)$.
\end{corollary}
